### 2015-06-22 text/ms.Rmd
Edit discussion

>>>>

Ensemble models provide a useful approach to situations where conservation and management decisions must be made on the basis of multiple, potentially contrasting estimates of status---a situation that is common to many ecological settings beyond fisheries. Compared to individual models of fish population status, ensemble models were consistently the best or among the best across three performance dimensions, two response variables, two datasets, and multiple ensemble model types. Our results suggest choosing an ensemble model that allows for non-parametric relationships, such as machine learning methods---these methods provide added insight into individual model behaviour and generally performed the best---but even a simple average of predictions across multiple models may be useful.

Certain conditions will make some ensemble models more effective than others. First, ensemble models will be most effective when they are comprised of diverse individual models that make substantially different assumptions about underlying dynamics, or make different but plausible assumptions about certain parameter values [e.g. @ali1996; @tebaldi2007]. Such models would be expected to perform well across different conditions and an ensemble model can exploit the best predictive performance of each model. Second, ensemble models will be most effective when they are not overfit to training data. The probability of overfitting ensemble models generally increases with the number of individual models [e.g. @caruana2004]. Cross-validation testing, information theoretic methods (e.g. AIC), and methods that are robust to over-fitting such as random forests (REF), may help avoid overfitting ensemble models. We note that our simplest ensemble model, a mean of the individual model predictions, performed approximately as well as the complex machine learning models when we applied our ensembles to an entirely new dataset (FIG). Third, ensemble models will be most effective when they are trained on data that are representative of the dataset of interest. Cross-validation within a training dataset will provide a optimistically biased impression of predictive performance if the training dataset fundamentally differs from the dataset of interest.

Ensemble models share similarities with coefficient averaging (Burnham and Anderson REF) but differ in many important way. At a high level, ensemble models and coefficient averaging share the same idea that no one model is correct and multiple models can contribute useful information for inference. A fundamental difference between coefficient averaging and ensemble models is that coefficient averaging focuses on a averaging *coefficients* whereas ensembles instead average *predictions*. By focussing on predictions, ensembles are a more general purpose tool: they don't require information theoretics, they can combine completely different types of models (e.g. combining parametric and non-parametric models or frequentist and Bayesian predictions), and they can combine predictions in complex non-linear ways that also depend on additional covariates.

A strength of ensemble models is that they can be tailored or specific response variables. For example, we built separate models of mean \bbmsy\\ and the slope of \bbmsy\\. The same set of model weights or non-linear relationships need not hold across different response variables. Ensemble models can optimally combine the individual models depending on the response. Ensemble models could be combined to estimate any number of response variables of interest. For example, they could be combined to estimate a binary response such as whether status is above or below some threshold.

* Coilin: How ensembles can help understand mechanistic underpinnings of individual 
  models
    * discover surprises: counterintuitive relationships and interactions
    * can dig into surprising conditions and learn about why certain models fail; 
      potentially learn how to improve models
    * can learn under what conditions certain models perform well
    * pick out an example

* Jim: Other possible applications of ensemble models outside fisheries status and
  trajectory
    * other taxa examples
    * other kinds of response variables

<!--
* Other possible topics:
    * how much better are the ensembles really? translate the results into
      some concrete examples in an absolute not relative sense
    * other types of ensembles: assigning weights, incorporating uncertainty
      around estimates, GAMs, ...
    * when wouldn't you want to use ensembles? perhaps if models represent 
      dichotomous assumptions where either one or the other is right and imply
      different management actions? ...
    * your ideas here...
-->

# References
